Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-12 paper/paper.tex
Add GD affiliations

\author{Elvis Dohmatob, Guillaume Dumas, Danilo Bzdok\\
  \textbf{Please add your affiliation}
  %% INRIA, Parietal team, Saclay, France\\
  %% CEA, Neurospin, Gif-sur-Yvette, France\\
  %% firstname.lastname@inria.fr
}

@@

\begin{abstract}
The default mode network (DMN) is believed to subserve the human
baseline mental activity.
%
Many research streams converge to its likely role in evolutionarily adaptive
envisioning of mental scenarios to simulate the future.
Such functional roles become more likely due to
this brain network's highest energy consumption in the brain and
its intimate coupling with conscious awareness
\textbf{(XXX Guillaume: It escaladed quickly.)}.
%
The present concept paper proposes a \textit{process model}
in trying to explain \textit{how} the DMN may actually implement continuous
assessment and prediction of the environment to guide action choices.
DMN function is recast in the mathematical terms of
control theory and reinforcement learning based on Markov decision processes.
We argue that our formal account of DMN function
naturally accommodates
previously proposed cognitive accounts as special cases and
parsimoniously explains
experimental findings in animals and humans.
%
A process models for the neural implemention
of continuous future predictions probably realized in the DMN
could offer insight into the statistical mechanisms underlying human behavior.
\end{abstract}

>>>>

\author{Elvis Dohmatob, Guillaume Dumas, Danilo Bzdok\\
  \textbf{Please add your affiliation}
  %% INRIA, Parietal team, Saclay, France\\
  %% CEA, Neurospin, Gif-sur-Yvette, France\\
  %% firstname.lastname@inria.fr
  %% GD1 Institut Pasteur, Human Genetics and Cognitive Functions Unit, Paris, France
  %% GD2 CNRS UMR 3571 Genes, Synapses and Cognition, Institut Pasteur, Paris, France
  %% GD3 University Paris Diderot, Sorbonne Paris Cité, Paris, France
  %% GD4 Centre de Bioinformatique, Biostatistique et Biologie Intégrative (C3BI, USR 3756 Institut Pasteur et CNRS), Paris, France
}

@@

\begin{abstract}
The default mode network (DMN) is believed to subserve the human
baseline mental activity.
%
Many research streams converge to its likely role in evolutionarily adaptive
envisioning of mental scenarios to simulate the future.
Such functional roles become more likely due to
this brain network's highest energy consumption in the brain and
its intimate coupling with conscious awareness.
%
The present concept paper proposes a \textit{process model}
in trying to explain \textit{how} the DMN may actually implement continuous
assessment and prediction of the environment to guide action choices.
DMN function is recast in the mathematical terms of
control theory and reinforcement learning based on Markov decision processes.
We argue that our formal account of DMN function
naturally accommodates
previously proposed cognitive accounts as special cases and
parsimoniously explains
experimental findings in animals and humans.
%
A process models for the neural implemention
of continuous future predictions probably realized in the DMN
could offer insight into the statistical mechanisms underlying human behavior.
\end{abstract}
